Tor's Usability for Censorship Circumvention

### 2015-10-09 paper/circumvention-experiment.tex
(non-atomic) reformatting intro setion, added motivation section to intro, hacked out the configuration dialogue section

\section{Tor's Usability}
As the most widely used anonymity tool today, Tor is primarily known for this aspect of its functionality.
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later.

There are still many features of Tor that are left unevaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation,
we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface (Figure
~\ref{fig:interface}) to guide users through setting up their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both.

Our study will test this hypothesis by measuring if the connection
interface successfully guides users to correctly configuring their browser.\\

@@

@@

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface. Tor users in censored environments and some of our participants
    will be required to select the correct bridge for circumventing censorship.
    Note that the interface prompts users to choose a transport type, which can be
    the source of confusion. Bridges are non-listed guard relays to the Tor
    network; transports, supported by bridges, obfuscate traffic in
    different ways.}
\end{figure}

>>>>

\section{Tor}
\noindent {\bfseries Usability}
Tor is primarily known as the most widely used anonymity tool today. 
For this reason, user studies on Tor have been solely about the usability of Tor as an
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later. \\

\noindent {\bfseries Scoping}
There are still many features of Tor that are left unevaluated through user
research --- such as advanced web tasks (e.g., accessing hidden services), the
configuration menu to connect to the Tor network, configuring automatic
updates, and identity/cookie management. Rather than selecting the features to
study in isolation,
we decided to focus on an important use case of Tor browser: censorship circumvention. 
Internet censorship is pervasive across the world today \cite{faris2008measuring}, with 
some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.\\

\noindent {\bfseries Motivation}
Changing the configuration interface would not require changes to the 
Tor Browser functionality, making any suggested improvements very practical to 
deploy in a short period of time. {\color {red} Additionally, people are just literally
being censored everywhere so a lot of people are using it for this purpose. So 
we want this to be usable for that purpose.}

@@

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface (Figure
~\ref{fig:bridges}) to guide users through setting up their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both. 
%definition of a bridge, defintion of a proxy here. 
Our study  will explore how well this interface successfully guides users to 
correctly configuring their browser.\\

\begin{figure}[h]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface. Tor users in censored environments and some of our participants
    will be required to select the correct bridge for circumventing censorship.
    Note that the interface prompts users to choose a transport type, which can be
    the source of confusion. Bridges are non-listed guard relays to the Tor
    network; transports, supported by bridges, obfuscate traffic in
    different ways.}
\end{figure}

\noindent {\bfseries Configuration Flow}
{\color {red}

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Path 1}:  Configure directly
\item {\bfseries Path 2}:  Bridge, no proxy
\item {\bfseries Path 3}:  Bridge, proxy 
\item {\bfseries Path 4}:  No bridge, proxy
\item {\bfseries Path 5}:  No bridge, no proxy
\end{itemize}

Upon the startup of the configuration interface, a user is asked to describe their 
current situation. If their Internet connection is censored or proxied, the user 
clicks ``Configure'' to configure bridge and proxy settings. Otherwise, the user
clicks ``Connect'' to connect directly to the Tor network.

If a user is not connecting directly to the Tor network, then they are asked to 
configure a bridge (as seen in TODO, the title of the window during configuration 
is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
first before a proxy is that more people need to configure bridges than proxies,
but this is not known. The bridge configuration asks the users if their ISP blocks
or censors connections to the Tor Network. The assumption here is that users will 
not know if they need a bridge or not, but that they are equipped to answer if their
current network environment censors the Tor Network. The configuration interface 
uses this answer to deem if the user needs a bridge. A yes to this question would
require a bridge while a no to this question would not. If they answer yes, they are 
asked to configure the bridges. If they answer no, then the configuration interface 
moves on to configuring proxies.

If a user who is not directly connecting to the Tor network is finished configuring
a bridge or has answered that they do not need a bridge, they are asked to 
configure a local proxy (as seen in TODO, the title of the window during
configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
users if they need to use a local proxy to access the Internet. The assumption 
is that people will not know the answer to this question, so there is a text instructing
users how to find the answer to this question below the question. If the answer to
the question is yes, the user needs a proxy and is taken to a screen where they are
asked to configure the proxy settings. If the user does not need a proxy, then the 
configuration interface attempts to connect to the Tor network with all the 
given inputs up to this point so far.

Note that a user can decide to click ``Configure'' because they believe the 
Internet connection is censored or proxied, but then answer the bridge and proxy
questions in such a way that they deemed that they do not need a bridge or proxy 
after all. In this case, clicking the ``Connect'' button after the above configuration steps
would be equivalent to clicking ``Connect'' on the first screen. \\

}

@@

\noindent {\bfseries Things that are good} %% fix this so it's not so casual
{\color {red} 
Talking to users, ``this will work in most situations,'' help button, support email.
putting the bridge configuration before the proxy, etc.... \\
}

\noindent {\bfseries Things that could be improved}%% fix this so it's not so casual
{\color {red} 
clarify between bridges and proxy, getting rid of redundant text, etc.  \\
}

@@
